---
title: |
The Pipes in the p-values: American Statistical Association Enters into Public Brawl \
  with American Plumbers Association
subtitle: "A case study"
short-title: "ASA Brawl"
published: "Under review at *American Plumbers Association*"
code-repo: "Access the code, data, and analysis at <https://git.apa.ufp/rcoeff/asa-brawl>"
correspondence-prefix: "Correspondence concerning this article should be addressed to"
author:
  - name: Robert Coefficient
    email: rcoefficient@apa.com
    orcid: 0009-0003-6465-6658
    title: Chief Statistical Officer
    affiliations: 
      - id: APA
        name: American Plumbers Association
        department: Office of the CSO
        address: 1234 Main Street
        city: Anytown
        region: NY
        country: USA
        postal-code: 12345
    attributes:
      corresponding: true
  
abstract: |
  The American Plumbers Association contends with the American Statistical Association over the use of *p*-values. The public brawl was televised and many statisticians were injured as a result of the pipe-throwing and p-trapping show of force of the APA.
thanks: |
  Placeholder text generated at https://www.feedough.com/paragraph-generator/.
additional-info: |
  We have severe conflict of interests in this matter.
keywords:
  - p-values
  - statistics
  - plumbing
date: August 23, 2024
epigraph:
  - text: p-values are like coupons:\
          tempting to use, and lead to overspending. 
    source: Chad Grayson (PT)
bibliography: references.bib
csl: csl/ama.csl
format:
  fair_adam-pdf: default
  #fair_adam-manuscript-pdf: default
  #fair_adam-manuscript-docx: default
---

In a surreal clash of worlds, the American Plumbers Asso-ciation found itself entangled in a heated, publicized brawl with the American Statistical Association over the contentious use of p-values, plunging into a chaotic verbal sparring match that ri-valed the battles of ancient gladiators. 

# Main section

As cameras rolled and on-lookers gawked, the two organizations exchanged blows of data analysis versus pipefitting expertise, their arguments echoing through the halls of academia with a cacophony of conflicting ideologies. The clash evolved into a spectacle of intellectual ac-robatics, with metaphors as sharp as cutters and wit as quick as leaks. Amidst this clash of titans, the audience found themselves caught in a whirlpool of statistical significance and plumbing precision, witnessing a showdown where the flow of information intersected with the flow of water in a metaphorical dance of chaos and order. The unexpected confrontation became a caution-ary tale of the perils of miscommunication [@anderson2024], where the pipes of logic clashed with the valves of probability, leaving behind a trail of confusion and amusement in its wake.
In an unexpected turn of events during the televised event, the President of the American Statistical Association (ASA) found himself flat on the mat within a mere 30 seconds of the physical exchange commencing. Astoundingly, raw muscle triumphed over brain matter as the towering opponent delivered a knockout blow that left the audience in stunned silence [@gonzalez2024]. The juxtaposition of statistical prowess and physical prowess con-verged in a moment that can only be described as a metaphorical clash between calculation and brute force. It was a humbling re-minder that in the ring of life, sometimes numbers and formulas pale in comparison to the primal instinct of survival [@smithson2024]. It was a jaw-dropping example of how within those fleeting moments, brawn outshone brains, leaving a lasting impression that strength isn't always measured in graphs and charts, but in the resilience of the human spirit.

```{r}
p_traps <- function(p,traps){
  p * traps
}
# how many p-traps were thrown?:
total_p_traps_thrown <- p_traps(3,5)
```

In the chaotic aftermath of the epic clash between the American Plumbers Association and the American Statistical Association [@kline2024], the collateral damages painted a vivid picture of mayhem and disarray.

The following damages were caused: 
1.	Burst pipes and flooding.
2.	Sewage seeped into the cracked pavements and shattered windows.
3.	The clash of wrenches and calculators

$$
y = \text{cost_of_damages} + \beta_1 p -\beta_2wrenches + \beta_3calculators + \beta_4\text{broken_windows}
$$

In the epic clash between the American Plumbers Association and the American Statistical Association over the significance of p-values, the dust has settled, revealing a landscape for-ever changed. The stark divide between the practical world of pipes and wrenches and the abstract realm of probabilities has been bridged, leaving a new path forward. No longer are p-values seen as mere gatekeepers of statistical significance [@yamamoto2024], but rather as dynamic tools in the plumber's toolbox, guiding decisions with precision and foresight. Like a master plumber wielding a wrench with skill and finesse, the statistical practitioner navigates the murky waters of data analysis, shaping outcomes with a deft touch. The once disparate disciplines now dance in harmonious synergy, their unique strengths merging to form a formidable union. As the curtain falls on this turbulent chapter, the true victor emerges not as a single association [@nguyen2024], but as a collective force of innovation and collaboration, paving the way for a future where the flow of information runs clear and true.

## Visualize it

```{r plot-p-traps}
#| echo: false
#| label: fig-np-traps
#| fig-cap: Too many p-traps thrown
#| fig-align: "center"
par(mar = c(0, 1, 1, 0))
plot(x = seq(1:total_p_traps_thrown), col = "darkgoldenrod1", 
     pch = 19,axes = TRUE, xlab = "", ylab = "")
```

### Third level heading

Like a master plumber wielding a wrench with skill and finesse, the statistical practitioner navigates the murky waters of data analysis, shaping outcomes with a deft touch. The once disparate disciplines now dance in harmonious synergy, their unique strengths merging to form a formidable union. As the curtain falls on this turbulent chapter, the true victor emerges not as a single association [@nguyen2024], but as a collective force of innovation and collaboration, paving the way for a future where the flow of information runs clear and true.

#### Fourth level heading

The clash between the American Plumbers Association and the American Statistical Association, once marked by tension and rivalry, has ultimately forged a new understanding—one where practical application meets analytical rigor.